The Multi-Stencil Language

### 2016-05-30 ARTICLES/IJPP/article/introduction.tex
IJPP article intro

As the computation power of modern high performance architectures increases, their heterogeneity and complexity also become more important. For example, the current world's top supercomputer Tianhe-2~\footnote{url{www.top500.org}} is composed of multi-cores processors and accelerators, and is able to reach a theoretical peak performance around thirty floating point operations par seconds. However, to be able to use such a machine, multiple programming models, such as MPI (Message Passing Interface), OpenMP, CUDA etc., and multiple optimization techniques, such as cache optimizations or vectorization optimizations, have to be combined. Moreover, current architectures evolution lets think that heterogeneity and complexity in HPC will continue to grow in future.

>>>>

As the computation power of modern high performance architectures increases, their heterogeneity and complexity also become more important. For example, the current world's top supercomputer Tianhe-2~\footnote{url{www.top500.org}} is composed of multi-cores processors and accelerators, and is able to reach a theoretical peak performance around thirty peta floating point operations par seconds. However, to be able to use such a machine, multiple programming models, such as MPI (Message Passing Interface), OpenMP, CUDA etc., and multiple optimization techniques, such as cache optimizations or vectorization optimizations, have to be combined. Moreover, current architectures evolution lets think that heterogeneity and complexity in HPC will continue to grow in future.
